---
title: "Research: Open Source Substrate Blockchain Explorer Compatible With Phala Network"
author: "Emmanuel O."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
if (!require("XLConnect")) { install.packages("XLConnect") }
library(XLConnect)
```


```{r}
workbook <- loadWorkbook("candidates.xlsx", create = TRUE)
candidates <- readWorksheet(
  workbook, sheet = "candidates", startRow = 1,
  startCol = 1, endRow = 6, endCol = 4, header = TRUE
)

techstack <- readWorksheet(
  workbook, sheet = "techstack", startRow = 1,
  startCol = 1, endRow = 5, endCol = 4, header = TRUE
)

community <- readWorksheet(
  workbook, sheet = "community", startRow = 1,
  startCol = 1, endRow = 5, endCol = 6, header = TRUE
)

codequality <- readWorksheet(
  workbook, sheet = "codequality", startRow = 1,
  startCol = 1, endRow = 5, endCol = 7, header = TRUE
)

devops <- readWorksheet(
  workbook, sheet = "devops", startRow = 1,
  startCol = 1, endRow = 5, endCol = 4, header = TRUE
)

features <- readWorksheet(
  workbook, sheet = "features", startRow = 1,
  startCol = 1, endRow = 5, endCol = 8, header = TRUE
)

transaction_features <- readWorksheet(
  workbook, sheet = "transaction_features", startRow = 1,
  startCol = 1, endRow = 5, endCol = 5, header = TRUE
)

event_features <- readWorksheet(
  workbook, sheet = "event_features", startRow = 1,
  startCol = 1, endRow = 5, endCol = 5, header = TRUE
)

statistics_features <- readWorksheet(
  workbook, sheet = "statistics_features", startRow = 1,
  startCol = 1, endRow = 5, endCol = 4, header = TRUE
)
```

# Research: Open Source Substrate Blockchain Explorer Compatible With Phala Network

This research is not intended to diminish the work of the teams or contributors to the particular Block Explorer project. It is conducted for research purposes only.

## List of candidates

The Dotscanner block explorer will not be analyzed any further, since it is not an open source solution. 

```{r}
knitr::kable(candidates, col.names = gsub("[.]+", " ", colnames(candidates)))
```

## Tech stack

```{r}
knitr::kable(techstack, col.names = gsub("[.]+", " ", colnames(techstack)))
```

## Community

```{r}
knitr::kable(community, col.names = gsub("[.]+", " ", colnames(community)))
```

## Code quality

```{r}
knitr::kable(codequality, col.names = gsub("[.]+", " ", colnames(codequality)))
```

## Devops

```{r}
knitr::kable(devops, col.names = gsub("[.]+", " ", colnames(devops)))
```

## Features

```{r}
knitr::kable(features, col.names = gsub("[.]+", " ", colnames(features)))
```

### Transaction features

```{r}
knitr::kable(transaction_features, col.names = gsub("[.]+", " ", colnames(transaction_features)))
```

### Event features

```{r}
knitr::kable(event_features, col.names = gsub("[.]+", " ", colnames(event_features)))
```

### Statistics features

```{r}
knitr::kable(statistics_features, col.names = gsub("[.]+", " ", colnames(statistics_features)))
```

## Conclusion 

SUBSCAN appears to be the block explorer into which the Phala network can be integrated. It is well documented and maintained, has a high code quality and meets almost all features of the evaluation.

## Deployment Guide 

The network will be included by SUBSCAN. Therefore a form has to be filled. 

**https://subscan.typeform.com/to/jqdAWJ?typeform-source=www.subscan.io**
