---
title: "Research: Open Source Substrate Blockchain Explorer Compatible With Phala Network"
author: "Emmanuel O."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
if (!require("XLConnect")) { install.packages("XLConnect") }
library(XLConnect)
```


```{r}
workbook <- loadWorkbook("candidates.xlsx", create = TRUE)
candidates <- readWorksheet(
  workbook, sheet = "candidates", startRow = 1,
  startCol = 1, endRow = 6, endCol = 4, header = TRUE
)

techstack <- readWorksheet(
  workbook, sheet = "techstack", startRow = 1,
  startCol = 1, endRow = 5, endCol = 4, header = TRUE
)

community <- readWorksheet(
  workbook, sheet = "community", startRow = 1,
  startCol = 1, endRow = 5, endCol = 6, header = TRUE
)

codequality <- readWorksheet(
  workbook, sheet = "codequality", startRow = 1,
  startCol = 1, endRow = 5, endCol = 7, header = TRUE
)

devops <- readWorksheet(
  workbook, sheet = "devops", startRow = 1,
  startCol = 1, endRow = 5, endCol = 4, header = TRUE
)

features <- readWorksheet(
  workbook, sheet = "features", startRow = 1,
  startCol = 1, endRow = 5, endCol = 8, header = TRUE
)

transaction_features <- readWorksheet(
  workbook, sheet = "transaction_features", startRow = 1,
  startCol = 1, endRow = 5, endCol = 5, header = TRUE
)

event_features <- readWorksheet(
  workbook, sheet = "event_features", startRow = 1,
  startCol = 1, endRow = 5, endCol = 5, header = TRUE
)

statistics_features <- readWorksheet(
  workbook, sheet = "statistics_features", startRow = 1,
  startCol = 1, endRow = 5, endCol = 4, header = TRUE
)
```

# List of candidates

```{r}
knitr::kable(candidates, col.names = gsub("[.]+", " ", colnames(candidates)))
```

# Tech stack

```{r}
knitr::kable(techstack, col.names = gsub("[.]+", " ", colnames(techstack)))
```

# Community

```{r}
knitr::kable(community, col.names = gsub("[.]+", " ", colnames(community)))
```

# Code quality

```{r}
knitr::kable(codequality, col.names = gsub("[.]+", " ", colnames(codequality)))
```

# Devops

```{r}
knitr::kable(devops, col.names = gsub("[.]+", " ", colnames(devops)))
```

# Features

```{r}
knitr::kable(features, col.names = gsub("[.]+", " ", colnames(features)))
```

## Transaction features

```{r}
knitr::kable(transaction_features, col.names = gsub("[.]+", " ", colnames(transaction_features)))
```

## Event features

```{r}
knitr::kable(event_features, col.names = gsub("[.]+", " ", colnames(event_features)))
```

## Statistics features

```{r}
knitr::kable(statistics_features, col.names = gsub("[.]+", " ", colnames(statistics_features)))
```

# Conclusion 

SUBSCAN seems to be the block explorer that the Phala network should be integrated with. It is well documented and maintained, has a high code quality and matches almost all features of the assessment.

# Deployment Guide 

The network will be included by SUBSCAN. Therefore a form has to be filled. 

**https://subscan.typeform.com/to/jqdAWJ?typeform-source=www.subscan.io**
